\documentclass{ccg-topic}

\topic{Weeks 11 and 12}

\institution{University of Colorado}
\coursenum{MATH 2510}
\coursename{Introduction to Statistics}
\semester{Fall 2019}
\author{Joseph Timmer (Edited by Colton Grainger)}
\date{\today}
\email{colton.grainger@colorado.edu}
\thanks{This material corresponds to Chapter 8 of \emph{Understandable Statistics} [Brase and Brase, 2018].}

\usepackage{graphicx, color}
\newcommand{\answer}[1]{\color{black}#1}
\begin{document}
\frontstuff

\setcounter{section}{-1}

\section{Definitions}
After reading through Brase and Brase Chapter 8, know the definitions of the following.%
    \footnote{%
``If you are like me,  you may also despise the memorization aspect of math.  I've always disliked how tests force you to memorize.  But we need a common and efficient language to speak of complex ideas, and this section is meant to make sure that you can communicate using the language on which English-speaking mathematicians have come to agree.  Moreover, I hope that some of these ideas become intuitive enough that you will even be able to guess the correct definition, based on how we have come to know these words.'' [Hiro Lee Tanaka, Algebra 122 Midterm Review Notes, 2014]
    }

    \begin{enumerate}
    
        \item null hypothesis
        
        \item alternate hypothesis
        
        \item $p$-value 

        \item $\alpha$, the level of significance.
        
        \item error type
        
        \item test type (determined by $H_1$)
        
        \item $z$ (standard normal) tests

        \item $t$ (student's $t$) tests

        \item rejecting the null hypothesis $H_0$ when $p \le \alpha$
            
        \item paired versus unpaired data

        \item tests for which $H_0: \mu = 0$ is \textbf{always} the null hypothesis
            
    \end{enumerate}

\newpage
\section{Lecture Outlines}
\subsection*{Hypothesis Testing}

In Chapter 7, we estimated the value of population parameters (mean and proportion) using confidence intervals. Another method of statistical inference is to make decisions concerning the value of a population parameter, which we do in Chapter 8 with hypothesis testing.

\begin{enumerate}

  \item Suppose that you roll a regular six-sided die 600 times. About how many times would you expect to see a 4 rolled within those 600?
    
    \begin{enumerate}
    
      \item If you saw 105 rolls that were 4, would this be surprising\ldots enough to question the fairness of the die?

      \item What if you saw 595 rolls that were 4, would this be surprising\ldots enough to question the fairness of the die?

      \item Where would you draw the line between ``not so surprising" and ``surprising"?
      
    \end{enumerate}
    
  \item The basic idea in hypothesis testing is to start with an assumption of what ''should" happen and to draw a line on what extreme outcomes would be ``surprising". If the random sample indicates a ''surprising" result, we have evidence to abandon our assumption\ldots if the ransom sample indicates a ``not so surprising" result, we do not have adequate evidence to abandon our assumption and we must stick with it.
  
  \item Note, as with the case of the rolls of the die, the result of the random sample may be very ``surprising" (595 of our 600 rolls were 4), but it will never serve as PROOF that our assumption is wrong (as it's possible that this 595/600 happens with a completely fair die).
  
\end{enumerate}

\subsection*{8.1 Introduction to Statistical Tests}

\begin{enumerate}

  \item This section introduces the language and formalizes the concepts of ``drawing a line" and interpreting the results of the test.
  
  \item When reading, pay close attention to
  
    \begin{enumerate}
    
      \item The notation and definition/usage of the null hypothesis and the alternate hypothesis. 
      
      \item How we categorize the test as right-tailed, left-tailed, or two-tailed.
      
      \item What the P-value measures and how it is used to draw the conclusion of the test.
      
      \item The usage and meaning of the conventional language of ``Reject $H_0$" and ``Fail to Reject $H_0$".
      
    \end{enumerate}
    
\end{enumerate}

\subsection*{8.2 Testing the Mean}

\begin{enumerate}

  \item The calculator functions that will be useful are \texttt{Z-Test} and \texttt{T-Test}. Like \texttt{Z-Interval} and \texttt{T-Interval}, one is used with $\sigma$ is known and the other when $\sigma$ is unknown.
  
  \item One may find the ``critical regions" method helpful in solidifying the concepts of hypothesis testing, but one will be required to compute and interpret P-values as well. So, this ``critical regions" method should be considered a secondary method.
  
\end{enumerate}

\subsection*{8.3 Testing the Proportion}

The calculator function that will be useful is \texttt{1-PropZTest}.

\subsection*{8.4 Paired Data}

\begin{enumerate}

    \item A discussion of dependent (paired) versus independent data will need to be had.  We treat paired data quite differently than independent data.
    
    \item A good guideline is the following: If you implement two distinct processes on \textbf{the same group} of individuals, then the data is paired.
    
    \item When the data can be paired, the null hypothesis is always that the mean of the differences is 0 (there is no difference).
    
    \item One will need to created a ``new" data set that is the list of differences of the pairs---then use T-Test to complete the test. By typing $L_1 - L_2$ in the label of the stats editor will generate a difference column.
    
\end{enumerate}

\subsection*{8.5 Independent Populations}

\begin{enumerate}

    \item Here the null hypothesis is always that the difference of the means (or proportions) is 0 (there is no difference).
    
    \item The \texttt{2-SampZTest}, \texttt{2-SampTTest}, and \texttt{2-PropZTest} are the key calculator functions.
    
    \item Computations are easy with the calculator\ldots reading and deciphering which function does the job for a specific problem is the tough part.

\end{enumerate}

\newpage
\section{Worksheet: Testing the Mean}
\input{Worksheet_Sec8_1_2.tex}

\newpage
\section{Worksheet: Testing the Proportion}
\input{Worksheet_Sec8_3.tex}

\newpage
\section{Worksheet: Paired Data}
\input{Worksheet_Sec8_4.tex}

\newpage
\section{Worksheet: Independent Populations}
\input{Worksheet_Sec8_5.tex}

\end{document}
