\documentclass{article}
\usepackage{graphicx, color}


\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.0in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\parskip}{2ex}
\setlength{\parindent}{0in}

%To display answers, replace "white" with "red" here;
\newcommand{\answer}[1]{\color{white}#1}

\begin{document}
\pagestyle{myheadings}\markright{
CU Boulder \hspace{0.5in} MATH 2510 - Introduction to Statistics }

\begin{center}
\textbf{\underbar{Worksheet 9 Exit Sheet}}
\end{center}

Moderator:{\underbar{\hspace{2in}}} \hfill  Recorder:{\underbar{\hspace{2in}} 

\bigskip

Reporter:{\underbar{\hspace{2in}}

As a group, come up with answers to the following questions.

\begin{enumerate}

    \item Two friends decide to compare their test results from their different math classes, the scores of which are normally distributed. Carla got a 87/100 on her exam. If the average of Carla's exam was a 72 with a standard deviation of 12, what would Carla's $z$-score be?
    
        {\answer Using the formula $z = \frac{x-\mu}{\sigma}$, Carla's score will be $\frac{87-72}{12} = \frac{15}{12} = \frac{5}{4} = 1.25.$}
    
    \vfill
    
    \item If Dennis got a 91/100 on his exam, should Dennis claim he did better on his exam? Explain why.
    
        {\answer At first glance, it appears Dennis's score is clearly better. However, we have yet to take into account the difficulty of their exams, which is what we will use the mean and standard deviation to measure...}
    
    \vfill
    
    \item Suppose Dennis' exam had a 80 average with a standard deviation of 11. Does this change your response in (b)?
    
        {\answer If we compute Dennis' $z$-score, we find $z = \frac{91-80}{11}=1$, so Carla's $z$-score his higher. This means, relative to their classmates, Carla did better on her exam.}
    
    \vfill
    
    \item Assuming the same average for Dennis' class, what would the standard deviation of Dennis' exam need to be for his score to match Carla's (with respect to their own classes)?
    
            {\answer We need to solve for $\sigma$ in $\frac{91-80}{\sigma} = \frac{87-72}{12} \Rightarrow \frac{11}{\sigma} = \frac{5}{4} \Rightarrow \sigma = \frac{44}{5} = 8.8$.}
    
    \vfill
    
\end{enumerate}
	
\end{document}